---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nicePlots

<!-- badges: start -->
<!-- badges: end -->

This package customizes ggplot2-plots for personal purposes. ``nicePlots`` generates clean and simple plots with some support for customization. Special attention has gone to provide intuitive support for grouping to plot trends, histograms and densities for separate subgroups. 

## Installation

You can install the development version of nicePlots from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SZuzek/nicePlots")
```

## Example

A basic example how to plot visually appealing graphs with two groups.

```{r example1}
library(nicePlots)
niceLinePlot(mtcars, "disp", "hp", linetype = "vs", linetypelabels = c("V-shaped", "straight"), linename = "Engine", line_size = 1.2, xlab = "Displacement, in litres", ylab = "Miles per Gallon, Highway")
```

``niceDensity`` can be used to inspect distributions.

```{r example2}
niceDensity(mtcars, "hp", color = "vs", fill = "vs", colorlabels = c("V-shaped", "straight"), colorname = "Engine", filllabels = c("V-shaped", "straight"), fillname = "Engine", xlab = "Miles per Gallon, Highway")

```


